### 2025-07-02 index.qmd
20250701 - citations & longitudinal random forest model

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "downlit", 
  "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "plotly", "quantmod", "fPortfolio", "NMOF", 
  "xts", "zoo", "forecast", "stringi", "parallel", "parallelly", "doParallel", #"webshot2"
  "missRanger", "ggridges", "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", 
  "remotes", "corrplot", "correlation", "mgcv", "rms", "car", "performance", 
  "lavaan", "mice", "miceadds", "interactions", "shiny", "PearsonDS", 
  "robustbase", "data.table", "future", "future.apply", "QuantPsyc", "SimDesign"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "xts", "zoo", "forecast", "stringi", "parallel", #"webshot2"
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", "caret", 
  "tidymodels", "LongituRF", "gpboost", "cmdstanr", "learnr", "remotes", 
  "corrplot", "correlation", "mgcv", "rms", "car", "performance", "lavaan", 
  "mice", "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", 
  "data.table", "future", "future.apply", "QuantPsyc", "SimDesign", "effectsize"
)

### 2025-07-02 machine-learning.qmd
20250701 - citations & longitudinal random forest model

```{r}
library("petersenlab")
library("parallel")
library("doParallel")
library("missRanger")
library("powerjoin")
library("caret")
library("gpboost")
library("tidyverse")
```

@@

```{r}
#| label: cross-sectional-machine-learning

@@

[@Hu2023]

library("LongituRF")

smerf <- LongituRF::MERF(
  X = seasonalData_subsetQB_imp$ximp[,c("passing_epa")] %>% as.matrix(),
  Y = seasonalData_subsetQB$fantasyPoints_lag,
  Z = seasonalData_subsetQB_imp$ximp[,c("pacr")] %>% as.matrix(),
  id = seasonalData_subsetQB$gsis_id,
  time = seasonalData_subsetQB_imp$ximp[,c("ageCentered20")] %>% as.matrix(),
  ntree = 500,
  sto = "BM")

smerf$forest # the fitted random forest (obtained at the last iteration)
smerf$random_effects # the predicted random effects for each player
smerf$omega # the predicted stochastic processes
plot(smerf$Vraisemblance) # evolution of the log-likelihood
smerf$OOB # OOB error at each iteration
```

>>>>

```{r}
library("petersenlab")
library("parallel")
library("doParallel")
library("missRanger")
library("powerjoin")
library("tidymodels")
library("LongituRF")
#library("caret")
library("gpboost")
library("tidyverse")
```

@@

```{r}
#| label: cross-sectional-machine-learning
#| eval: false

@@

Approaches to estimating random forest models with longitudinal data are described by @@Hu2023.
Below, we fit longitudinal random forest models using the `MERF()` function of the `LongituRF` package [@R-LongituRF].

```{r}
smerf <- LongituRF::MERF(
  X = data_train_qb_matrix %>% as_tibble() %>% dplyr::select(season:att_br.rush) %>% as.matrix(),
  Y = data_train_qb_matrix[,c("fantasyPoints_lag")] %>% as.matrix(),
  Z = data_train_qb_matrix[,c("pacr")] %>% as.matrix(),
  id = data_train_qb_matrix[,c("gsis_id")] %>% as.matrix(),
  time = data_train_qb_matrix[,c("ageCentered20")] %>% as.matrix(),
  ntree = 500,
  sto = "BM")

smerf$forest # the fitted random forest (obtained at the last iteration)
smerf$random_effects # the predicted random effects for each player
smerf$omega # the predicted stochastic processes
smerf$OOB # OOB error at each iteration
```

```{r}
#| label: fig-randomForestLongitudinalLogLikelihood
#| fig-cap: "Evolution of the Log-Likelihood."
#| fig-alt: "Evolution of the Log-Likelihood."

plot(smerf$Vraisemblance)
```
